%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{fontawesome}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Cheng-En Chiang \\ \vspace{1pt}
     \small \faPhone{ }(+886) 908055301 $|$ \href{andy06andy06@gmail.com}
     \faEnvelope{ \underline{r13631012@ntu.edu.tw}}  $|$
 \href{https://github.com/andy06andy06}
     \faGithub{ \underline{github.com/andy06andy06}}
    }
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {National Taiwan University \& University of Tsukuba }{}
      {Dual-Degree Program}{Dec. 2026(Expected)}
      \resumeItemListStart
        \resumeItem{National Taiwan University: Master of Science in Biomechatronics Engineering}
        \resumeItem{University of Tsukuba: Master of Agricultural Science in Agro-Bioresources Sciences and Technology}
          \resumeItem{Received \textbf{1 scholarship}}
      \resumeItemListEnd
    \resumeSubheading
      {National Taiwan University }{}
      {Bachelor of Science in Biomechatronics Engineering}{Sept. 2020 -- June 2024}
      \resumeItemListStart
        \resumeItem{Received \textbf{Dean's List Award\textbf{ }1 time} and \textbf{2 scholarships}}
        \resumeItem{Courses: Data Structures and Algorithms, Data Science, Linear Algebra, Machine Learning, Image Processing, Web Programming}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%---------------------------------

%-----------Work EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Lab of Machine Learning and Machine Vision, NTU}{}
      {Researcher, Server Administrator}{July 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Developed a pose estimation system using EfficientNet to track \textbf{16 keypoints} with \textbf{3.75 pixels RMSE}, and achieved \textbf{91\% accuracy} in classifying lameness across 32 pigs by integrating gait features with an SVM classifier.}
        \resumeItem{Administer a high-performance GPU cluster (6x NVIDIA RTX A6000) using Docker and Kubernetes, facilitating cloud computing resources and remote access for researchers at the University of Tsukuba.}
      \resumeItemListEnd
      \resumeSubheading
      {Bioproduction and Machinery Lab, UT}{}
      {Researcher}{April 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developed a behaviors monitoring system to observe piglets using YOLOv11 and EfficientNet-LSTM, achieved performance in detection, tracking, and behavior classification with \textbf{83.1\% MOTA}, and \textbf{93.0\% accuracy}.}
        \resumeItem{Conducted full-stack development workshops for lab members and a partner university in the Philippines, bridging the gap between research algorithms and deployable web applications.}
      \resumeItemListEnd
      \resumeSubheading
      {National Science and Technology Council}{}
      {Undergraduate Researcher}{July 2023 -- Feb. 2024}
      \resumeItemListStart
      \resumeItem{Applied machine learning, machine vision, and embedded system in pig farming industry.}
      \resumeItem{Integrated CNN architecture of U-Net with data analysis to establish a lameness detection system by tracking leg keypoints of pigs, replacing a pressure mat method which cost about \textbf{40,000 USD} for each mat.}
      \resumeItemListEnd
   \resumeSubHeadingListEnd
%--------------------------------------------

%-----------Publication-----------
\section{Publication}
      \resumeItemListStart 
        \resumeItem{Tsai, Y.J., \textbf{Chiang, C.E} et al. Monitoring the lactation-related behaviors of sows and their piglets in farrowing crates using
deep learning. Front. Anim. Sci. 5:1431285. doi: 10.3389/fanim.2024.1431285}
    \resumeItemListEnd
%---------------------------------------
    
%-----------Conference Experience-----------
\section{Conference Presentation}
      \resumeItemListStart
        \resumeItem{\textbf{Chiang, C.E}, Lin, E.C, Kuo, Y.F, "Lameness detection of gilts based on posture analysis using deep learning" [Oral presentation] XX CIGR World Congress 2026, Turin, Italy.}
        \resumeItem{\textbf{Chiang, C.E}, Lin, E.C, Kuo, Y.F, "A pig foot detection and tracking approach for gait evaluation " [Oral presentation] The 11th International Symposium on Machinery and Mechatronics for Agriculture and Biosystems Engineering, Bali, Indonesia.}
    \resumeItemListEnd
%---------------------------------------

%-----------PROJECTS-----------
\section{Projects \& Competition}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{National Field Robot Competition} $|$ \emph{YOLOv7, OpenCV, Python, PySerial, Arduino}}{}
          \resumeItemListStart
            \resumeItem{Applied YOLOv7 for fruit detection (\textbf{98.3\% mAP}, \textbf{99.1\% IOU}), enabling robust performance in outdoor field.}
            \resumeItem{Directed a \textbf{4-person software engineering team} to integrate computer vision into an autonomous filed robot.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Wordle Online Game} $|$ \emph{Next.js, Express.js, PostgresSQL, Tailwind CSS, WebSocket ,Git}}{}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{full-stack web application} using Express serving as RESTful API with Next.js as the framework.}
            \resumeItem{Implemented a dual-player mode using WebSocket, where players guess each other's question within limited time.}
            \resumeItem{Used Git for collaborative development with other 3 members, implementing horizontal division of project tasks.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Pineapple Growth Stage Classifier} $|$ \emph{Python, Pytorch, ResNet, OpenCV}}{}
          \resumeItemListStart
            \resumeItem{Trained a ResNet-18 model to classify different growth stages of pineapples which achieved an accuracy of \textbf{99.7\%}.}
            \resumeItem{Analyzed the result of the classifier and organized the findings using matplotlib and confusion matrix.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Remote Control Vacuum Car } $|$ \emph{Python, OpenCV, Arduino, Raspberry Pi }}{}
          \resumeItemListStart
            \resumeItem{Developed an autonomous vacuum cleaning robot capable of navigating obstacles and completing
cleaning tasks.}
            \resumeItem{Leveraged Arduino and Raspberry Pi to create a control system for the vacuum car, achieving maneuverability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI \& Computing}{: Pytorch, Tensorflow, CUDA, HuggingFace, TensorRT} \\
    }}
\small{\item{
     \textbf{Software Development}{: Python, C++, Java, Swift, JavaScript, HTML/CSS, React, Next.js} \\
    }}
\small{\item{
     \textbf{Infrastructure \& Data}{: Linux, Docker, Kubernetes, Git, MySQL, PostgreSQL, MongoDB, Arduino, Raspberry Pi} \\
    }}
    \small{\item{
     \textbf{Language}{: Mandarin(Native), English(Fluent, TOEIC L\&R 860), Japanese(Fluent, N1)} \\
    }}
 \end{itemize}
%-------------------------------------------
\end{document}
